Comparison of Fast, Hybrid Imaging Architectures for Multi-scale, Hierarchical Aperture Arrays

### 2024-10-02 response_to_review_1.txt

--> I thank the reviewer for a thorough review of the manuscript. I have addressed the concerns as detailed below. My responses are preceded with "-->". Changes in the manuscript have been highlighted with bold font. I hope this adequately addresses all the concerns and the manuscript is considered for publication.

@@

Title
- There's a misspelled word! (Hybrid)

--> Fixed.

Abstract
- I think the readability of the abstract could be improved. For example, the term "large-N" is a bit of jargon and I think the phrasing around this could be changed to more natural language.
- The use of "spatial scale" is similarly a bit jarring when first reading the paper. I think it's because the wording would more clearly be, for example, "...multiple spatial scales spanning the dimensions of individual elements, the size of stations (...), and the spacing between stations." (or similar)

Section 1
- First sentence, I think "polarizations" should be changed to "polarization states"

--> Changed as suggested.

- Later in the first paragraph, when mentioning the various classes of transient/variable sources, I think it would be good to include a representative range of timescales (duration and/or periodicity and/or duty cycle). Perhaps not very lengthy, but to give a sense of relevant timescales to be considered later in the paper. (This is included much later in Section 7.3 but should I think be included at some level here in the Introduction too.)
- Similarly at the end of the second paragraph I think you should give some indicative values for "large-scale structures" and "high sensitivity".

@@

Section 4
- First paragraph, the sentence starting "The second stage..." doesn't make sense, can this be reworded?

--> Reworded as suggested.

Figure 1
- "Accumulation" is misspelled in 6(?) places

--> Fixed the typos in the figure

Section 5
- In the first paragraph after equation (3), I think there’s an asterisk missing in the inline equation embedded in the sentence starting “For example, choosing…”
- In the next paragraph, I think “can hold any N_{a/s}” should be “can hold as many N_{a/s}”

--> Changed as suggested.

- In the next sentence, can you provide more about the constant padding factor (what is its role)?
